---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)

suppressPackageStartupMessages({
  library(flagon)
  library(magick)
})
```


# flagon

<!-- badges: start -->
![](http://img.shields.io/badge/cool-useless-green.svg)
<!-- badges: end -->

`flagon` provides PNG and SVG images of the flags of the world, indexed by 
their [2-letter ISO-3166 country codes](https://en.wikipedia.org/wiki/List_of_ISO_3166_country_codes).

The flags are sourced from [https://github.com/hjnilsson/country-flags](https://github.com/hjnilsson/country-flags), and are the public domain flag images from wikipedia.



## Installation

You can install from [GitHub](https://github.com/coolbutuseless/flagon) with:

``` r
# install.packages("remotes")
remotes::install_github("coolbutuseless/flagon")
```


## Usage: Retrieving filenames

```{r}
library(flagon)

country_codes <- c('au', 'dk') # Australia and Germany

flagon::flags(country_codes)
flagon::flags(country_codes, 'svg')
```


## Using with `magick`

```{r}
magick::image_read(flagon::flags('no'))
```


## That's it

That's all it does.

There's also a table of country codes (`flagon::country_codes`), 
the first rows of which are shown below:

```{r echo = FALSE}
flagon::country_codes %>%
  head %>%
  knitr::kable()
```

